Dataset-level report

### 2019-11-15 analysis/reports/dat_report_template.Rmd
update template to include heatmap

>>>>

Here is a heatmap of an observed + sampled FS:

```{r example heatmap}

a_fs_name <- cached(cache = cache)[ which(substr(cached(cache = cache), 0, 3) == "fs_")[1]]

fs_samples <- readd(a_fs_name, cache = cache, character_only = TRUE)

fs_heatmap <- ggplot(data = fs_samples, aes(x = rank, y = abund, group = sim, color = source)) +
  geom_line(alpha = .01) +
  geom_line(data = filter(fs_samples, source == "observed")) +
  theme_bw() +
  scale_color_viridis_d(end = .8)

fs_heatmap
